 
%---------------------------------------------------------------------------
% Content of Chapter 6 - Implementation
%
%---------------------------------------------------------------------------


\chapter{System deployment and testing}
\label{cha:deployment}

\chabstract{
Although the easiness of use was one of the most notable design goals, a description of deployment, usage, and example sessions is still needed. This chapter focuses solely on these issues. First I will try to cover basic deployment scenarios, from the simplest ones including only a single PC that runs all components - monitored application, Monitoring Hub and GUI up to a distributed approach where all components are spread across multiple hosts. Section~\ref{sec:ch7_working_with} describes roughly the use of the application - installation, starting up and describes in a few steps how to perform the most significant actions within the application. One should treat this section as a minimalistic approach to writing a user guide. The last section of this chapter covers the tests performed on the application. There were two types of tests performed - performance and usability-oriented. With a performance test, I would like to prove that there are no technical caveats when using the application. On the other hand, a usability test describes a real use case of the application, which aims at proving that the application is capable of helping on application performance analysis.

}


%---------------------------------------------------------------------------

\input{cha_depl/deployments}
\input{cha_depl/working_with}
\input{cha_depl/testing}

%---------------------------------------------------------------------------


